---
title: "Set4 Set5 Graph"

author: "Archana Raghu"
date: "11/7/2017"

output:
  html_document: default
  pdf_document: default
---

### Steps to create the Graduation Percentage based on Category graph

### Load the required Libraries and install the required packages

```{r}

library(readxl)	

library(ggrepel)

library(ggplot2)

```

### Loading the dataset 4

```{r}

setwd("~/Desktop/Nebraska education ")
Set_4 <- read_excel("~/Desktop/Nebraska education /Set 4.xlsx")
Graduation <- read_excel("Set 4.xlsx")
Grad <- Graduation
Grad[Grad == '-1'] <- NA
GradSet <- na.omit(Grad)
GradCln <- GradSet[c("Description","Graduation Count","Graduation Percentage")]

```

### Since there were around 13 description for all the students of a particular school, I have divided the dataset into three subsets based on their description.

### Creating subsets based on the category

```{r}

### Have grouped "Male" and "Female" description and created a subset Gender.

Gender <- GradCln[GradCln$Description == "Male" | GradCln$Description == "Female",]

### Have grouped all the Ethnic descriptions and created a subset Ethnic.

Ethnic <- GradCln[GradCln$Description == "Ethnic7 - Hispanic" | GradCln$Description == "Ethnic7 - American Indian/Alaska Native" | GradCln$Description == "Ethnic7 - Asian" | GradCln$Description == "Ethnic7 - Black or African American" | GradCln$Description == "Ethnic7 - Native Hawaiian or Other Pacific Islander" | GradCln$Description == "Ethnic7 - Black or African American" | GradCln$Description == "Ethnic7 - White" | GradCln$Description == "Ethnic7 - Two or More Races",]

### Have grouped all the remaining descriptions and created a subset Others.
 
Others <- GradCln[GradCln$Description == "Students eligible for free and reduced lunch" | GradCln$Description == "Special Education Students" | GradCln$Description == "English Language Learners",]

```

### Basic Plots and ggplot for for the category Gender

```{r}

Gender <- GradCln[GradCln$Description == "Male" | GradCln$Description == "Female",]

plot(Gender$`Graduation Percentage`, type="l", col="Pink")

plot(Gender$`Graduation Count`, type="l", col="Orange")

Plot1 <- ggplot(Gender, aes(x = Description, y = `Graduation Percentage`)) + theme(legend.position = "top", axis.text = element_text(size = 6))

(PLot1 <- Plot1 + geom_point(aes(color = `Graduation Count`), alpha = 0.5, size = 1.5, position = position_jitter(width = 0.25, height = 0)))

### Represented the high and low values using different colors

PLot1 + scale_x_discrete(name="Gender") + scale_color_continuous(name="",low="pink", high = "black")

### This plot shows the graduation percentage and count based on Gender categories.

### From the graph we can come to a conclusion that the "Male" and "Females" are almost but the males have a slightly high graduation percentage and count.

```

### Basic Plots and ggplot for for the category Ethnic

```{r}

Ethnic <- GradCln[GradCln$Description == "Ethnic7 - Hispanic" | GradCln$Description == "Ethnic7 - American Indian/Alaska Native" | GradCln$Description == "Ethnic7 - Asian" | GradCln$Description == "Ethnic7 - Black or African American" | GradCln$Description == "Ethnic7 - Native Hawaiian or Other Pacific Islander" | GradCln$Description == "Ethnic7 - Black or African American" | GradCln$Description == "Ethnic7 - White" | GradCln$Description == "Ethnic7 - Two or More Races",]

plot(Ethnic$`Graduation Percentage`, type="b", col="Orange")

boxplot(Ethnic$`Graduation Percentage`~Ethnic$Description)
	
ggplot(Ethnic,aes(x=`Graduation Count`))+ geom_histogram()
	
ggplot(Ethnic,aes(x=`Graduation Percentage`))+ geom_histogram()

Plot2 <- ggplot(Ethnic, aes(x = Description, y = `Graduation Percentage`)) + theme(legend.position = "top", axis.text = element_text(size = 6))

(PLot3 <- Plot2 + geom_point(aes(color = `Graduation Count`), alpha = 0.5, size = 1.5, position = position_jitter(width = 0.25, height = 0)))

### Represented the high and low values using different colors

PLot3 + scale_x_discrete(name="Ethnicity") + scale_color_continuous(low="blue", high = "red")

### This plot shows the graduation percentage and count based on the the Ethnic categories.

### From the graph we can come to a conclusion that the "Ethnic : Whites" have the highest graduation percentage and count.

```


### Basic Plots and ggplot for for the category Others

```{r}

Others <- GradCln[GradCln$Description == "Students eligible for free and reduced lunch" | GradCln$Description == "Special Education Students" | GradCln$Description == "English Language Learners",]

plot(Others$`Graduation Percentage`, type="p", col="Brown")

plot(Others$`Graduation Count`, type="l", col="Brown")

Plot5 <-  ggplot(Others, aes(x = `Graduation Percentage`, y = `Graduation Count`))

Plot5 + geom_line(aes(color = Description))

Plot5 <- ggplot(Others, aes(x = Description, y = `Graduation Percentage`)) + theme(legend.position = "top", axis.text = element_text(size = 6))

(Plot6 <- Plot5 + geom_point(aes(color = `Graduation Count`), alpha = 0.5, size = 1.5, position = position_jitter(width = 0.25, height = 0)))

### Represented the high and low values using different colors

Plot6 + scale_x_discrete(name="Other Category") + scale_color_continuous(name="",low="Orange", high = "Black")

### This plot shows the graduation percentage and count based the Other categories.

###From the graph we can come to a conclusion that the "Students eligible for free and reduced lunch" have the highest graduation percentage and count.

```
### Loading the dataset 5 

```{r}

setwd("~/Desktop/Nebraska education ")
Set_5 <- read_excel("~/Desktop/Nebraska education /Set 5.xlsx")
ELL <- read_excel("Set 5.xlsx")
ELL[ELL == '-1'] <- NA
ELLcln <- na.omit(ELL)
ELLcln[c("ELL Percentage","Dropout Rate")]
DropRate <- ELLcln[c("ELL Percentage","Dropout Rate")]

```

### Basic Plots and ggplot to see how the percentage of ELL affects the dropout rate

```{r}

boxplot(DropRate$`ELL Percentage`~ DropRate$`Dropout Rate`)

ggplot(DropRate, aes(x = `ELL Percentage`)) + geom_histogram()

ggplot(DropRate, aes(x = `Dropout Rate`)) + geom_histogram()

Plot7 <- ggplot(DropRate, aes(x = `Dropout Rate`, y = `ELL Percentage`)) + theme(legend.position = "top", axis.text = element_text(size = 6))

### This plot shows how the Dropout Rate is affected by the ELL Percentage.

plot(DropRate$`Dropout Rate`~DropRate$`ELL Percentage`, type="p", col="Red")

###From the graph we can come to a conclusion that the "Dropout Rate" of a school is high where the percentage of ELL is less and the Dropout Rate of the school is low where the ELL percentage is high. 

```



